---
title: "ARIMA Assignment"
output:
  html_document:
    df_print: paged
---

```{r}
library(fpp)
library(fpp2)
df <- read.csv("C:\\Users\\rusha\\Downloads\\BF\\HW files\\perrin-freres-monthly-champagne-.csv")
df_s<-df$Sales
columns_to_convert <- c("Year", "Month")
df[columns_to_convert] <- lapply(df[columns_to_convert], as.character)
time_index <- as.Date(paste(df$Year, df$Month, "01", sep = "-"))
ts_data <- ts(df$Sales, start = c(min(df$Year), min(df$Month)), frequency = 12)
plot(ts_data)
```
Output 
The time series data is seasonal 

```{r}
tsdisplay(ts_data)
```

```{r}
tsdiff1 <- diff(ts_data, differences = 1)
plot(tsdiff1)
```

```{r}
tsdisplay(tsdiff1)
```

```{r}
auto_fit <- auto.arima(ts_data, trace=TRUE, stepwise = FALSE)

```
Output summary 

ARIMA(1,0,0)(1,1,0)[12] with drift:
(1,0,0) represents the non-seasonal part of the model. The model includes one lag of the dependent variable 
(1,1,0) represents the seasonal part of the model. Indicates that first differences are taken at seasonal lag 12 because it is a monthly data with a seasonality of [12]
with drift: indicates that the model includes a drift term.
The model indicates that it considers the influence of both recent values and values from the same season in the previous year. 


```{r}
auto_fit
```

```{r}
attributes(auto_fit)
```
Q3) Perform and Plot the forecast for the next five periods

```{r}
plot(forecast(auto_fit,h=5,level=c(99.5)))

```
Q2) Residual analysis 
```{r}
Acf(ts_data)
```

```{r}
Acf(tsdiff1)
```

```{r}
Acf(auto_fit$residuals)
```

```{r}
plot.ts(residuals(auto_fit))
```

```{r}
hist(auto_fit$residuals)
```

```{r}
tsdiag(auto_fit)
```

```{r}
nsdiffs(ts_data)
```

```{r}
ndiffs(ts_data)
```

```{r}
ndiffs((diff(ts_data,4)))
```

```{r}
tsdisplay(diff(diff(ts_data,4)))
```

```{r}
fit3 <- auto.arima(ts_data,trace=TRUE, stepwise = FALSE )
```

```{r}
fit3
```

```{r}
Acf(fit3$residuals)
```

```{r}
plot.ts(residuals(fit3))
```

```{r}
hist(fit3$residuals)
```


```{r}
accuracy(auto_fit)
accuracy(fit3)
```

